Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
foo

The high-resolution data collected by activity-sensing devices, accumulated over a long period such as a patient's lifespan, can result in a substantially greater volume of data than current EHR platforms are designed to handle. To address this deficiency, we have devised a personal data platform ``WebBox \cite{webbox}'', optimised to handle the secure, long-term storage of structured data at large volume.  Thus far, WebBox has been used to archive clinician (hospital and GP-provided) data, including both raw structured data (such as clinical diagnostic results) and accompanying report documents.  Being optimised for structured data capture and integration, our current work extends this platform to the aforementioned activity profiles, created from retrieving raw sensed data from digital health device APIs and translating such observations to the Activity-SENSE representation.

>>>>

The high-resolution data collected by activity-sensing devices, accumulated over a long period such as a patient's lifespan, can result in a substantially greater volume of data than current EHR platforms are designed to handle. To address this deficiency, we have devised a personal data platform ``WebBox \cite{webbox}'', optimised to handle the secure, long-term storage of structured data at large volume.  Thus far, WebBox has been used to archive clinician (hospital and GP-provided) data, including both raw structured data (such as clinical diagnostic results) and traditional reports prepared by clinicians.  Being optimised for structured data capture and integration, our current work extends this platform to the aforementioned activity profiles, created from retrieving raw sensed data from digital health device APIs and translating such observations to the Activity-SENSE representation.
